Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-03-22 paper.Rmd
Adjusted size and caption for climate plot.

```{r climateplot, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("climateplot", "Temperature futures in two alternate realities."), fig.width=5, fig.height=5}
source("utils/climate_plot.R")
climate_plot() + theme(text=element_text(family='Palatino'))
```

>>>>

```{r climateplot, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("climateplot", "Historical measurements of temperature and temperature futures in two alternate realities."), fig.width=4, fig.height=3}
source("utils/climate_plot.R")
climate_plot() + theme(text=element_text(family='Palatino'))
```
